### 2020-02-17 Article.tex
Venga Alberto esta semana ya

We define the set of free variables of a formula as usual. 
We will use the notation $\phi(\overbar{y})$ to refer to a 
formula $\phi\in FO[\sigma]$
to denote that its free variables are the ones in $\overbar{y}$.
Formulas with no free variables are called sentences. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
formula, $\overbar{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overbar{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent 
	.Notice that those trees
	consist only of one vertex, their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

@@

\begin{lemma}
	Let $H$ be an hypergraph. Then 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
\end{lemma}
\begin{proof}

Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
$\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
$\overbar{h}$ be an ordering of the vertices
in $V(H)$. For any list 
$\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
let $X_{\overbar{v}}$ be the random indicator variable
that takes value $1$ if the natural map 
$f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
with probability
$ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
$
and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
copies of $H$ are in $G_n$. Thus, 
\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
\]
The expected number of copies of $H$ in $G_n$ is then this last
expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
In consequence,
\begin{align*}
&\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
\end{align*}
and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
\end{proof}

As a corollary of last result we get the following:  
\begin{lemma} 
	Let $H$ be an hypergraph such that $ex(H)>0$. Then
	a.a.s there are no copies of $H$ in $G_n$. 
\end{lemma}  
\begin{proof}
	Because of the previous fact, 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
	\xrightarrow[]{n\to \infty} 0$. Then an application of the first moment
	method yields the desired result. 
\end{proof}

The main theorem of this section is the following
\begin{theorem} \label{thm:simple}
	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
\end{theorem}

	The first moment method alone is not sufficient
	to prove our claim because the amount of dense 
	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
	in general. Thus, we need to prove that it suffices to
	prohibit a finite amount of dense sub-hypergraphs in order
	to guarantee that $G_n$ is $r$-simple.

\begin{lemma}
	Let $H$ be a dense hypergraph of radius $r$.
	Then $H$ contains a dense sub-hypergraph $H^\prime$ 
	with size no greater than
	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
\end{lemma}
\begin{proof}
	Choose $x\in V(H)$. Successively remove from $G$ edges $e$
	such that $d(x, e)$ is maximum until the resulting graph 
	$H^\prime$ has excess no greater than $0$. We have two cases:
	\begin{itemize}[leftmargin=*]
		\item $ex(H^\prime)=-1$. Let $e=[x_1, \dots, x_b]$ be
		the last removed edge and
		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
		For any $j=1,\dots, d$ choose 
		$P_j$ a path of size no greater than $r+1$ joining
		$x$ and $x_{i_j}$ in $H^\prime$.   
		Then $P_1\cup \dots P_d \cup e$ is a dense sub-hypergraph of $H$
		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
		\item $ex(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
		last removed edge. Continue removing the edges of $G^\prime$ 
		that are at maximum distance from $x$ until you obtain 
		$H^{\prime \prime}$ with $ex(H^{\prime\prime})=-1$. Let 
		$e_2=[y_1, \dots, y_{b_2}]$ be the last removed edge this time.
		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
		joining	$x$ and $x_{i_j}$ in $H^\prime$
		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
		and size less than $2r+2 + a$,
		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
	\end{itemize} 
\end{proof}

@@

@@

We define $\Lambda$ and $M$ as the minimal families
of expressions with arguments $\overbar{\beta}$ that satisfy
 the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
for any $b,i\in \N$ with $1\leq i \leq c$,
$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
the expression $(\beta_i/b) \prod_{j=1}^{a_i-1}\lambda_j$
belongs to $M$,  \textbf{(3)}
for any $\mu\in M$ and any $n\in \N$ both
$\mathrm{Poiss}_{\mu}(n)$ and $\mathrm{Poiss}_\mu(\geq n)$ are in $\Lambda$, 
and  \textbf{(4)} for any $\lambda_1,\lambda_2 \in \Lambda$, the
product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
\par
The goal of this section is to show  want to 
show that $\mathrm{Pr}[r,\mathcal{T}]$,
as an expression with parameters
$\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
$r$ and $\mathcal{T}$. The argument is as follows:
let $T:=N^{G_n}(v;r)$. \par

\begin{definition}

\end{definition}

\begin{lemma}
	Let $X\subset \N$ be a finite set of fixed vertices, and let 
	$r\in \N$. Define $G_n^\prime=G_n \setminus E(X)$.
	Then (1) a.a.s $G^\prime_n$ does not contain a path of size
	at most	$r+1$ between any two vertices $u,v\in X$, and (2)
	a.a.s $G^\prime_n$ does not contain a cycle of size $r+1$ 
	that contains a vertex $u\in X$.
\end{lemma}
\begin{proof}
	To prove the first part of the statement it suffices
	to show that the expected number of such paths
	tends to zero as $n$ tends to infinity. 
	Let $u,v$ be two vertices lying in $X$. 
	Given $f$ 	
\end{proof}

@@

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
		list of different vertices that are contained in $\overbar{w}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]		
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex, then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)=1. \]	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.  \par

>>>>

We define the set of free variables of a formula as usual. 
We will use the notation $\phi(\overbar{y})$ to refer to a 
formula $\phi\in FO[\sigma]$
to denote that its free variables are the ones in $\overbar{y}$.
Formulas with no free variables are called sentences and 
formulas with no quantifiers are called open formulas. \par
The quantifier rank of a formula $\phi$, denoted by $qr(\phi)$, 
is defined as the maximum number of nested quantifiers in $\phi$. \par
Sentences in $FO[\sigma]$ are interpreted over $\sigma$-structures
in the natural way. Given an structure $\mathcal{A}$, and a sentence
$\phi\in FO[\sigma]$ we write $\mathcal{A} \models \phi$ to denote 
that $\mathcal{A}$ satisfies $\phi$. If $\psi(\overbar{y})$ is a
formula, $\overbar{a}$ are elements in the universe of 
$\mathcal{A}$, and $\overbar{y}$ and $\overbar{a}$ are lists of the same size,
then we write $\mathcal{A} \models 
\psi(\overbar{a})$
to mean that $\mathcal{A}$ satisfies $\psi$ when the free variables in
$\overbar{y}$ are interpreted as the elements in $\overbar{a}$.
\todo[inline]{Deber\'a al menos mencionar un par de trabajos que estudien random k-SAT y propiedades a.a.s suficientes para no-satisfacibilidad}

@@

\begin{itemize}
	\item Any two trees with radius zero are $k$-equivalent.
	Notice that those trees
	consist only of one vertex: their respective roots.
	\item Suppose that the $k$-equivalence relation has been
	defined for rooted trees with radius at most $r$.
	\begin{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with radius
		at most $r+1$, and let $e_1, e_2$
		be initial edges of $T_1$ and $T_2$ respectively.
		Then $(T_1,e_1)\simeq_k (T_2,e_2)$ if
		$e_1$ and $e_2$ have the same color and there is a bijection 
		$f: e_1\rightarrow e_2$ between the vertices in $e_1$ and
		$e_2$ such that:
		\begin{itemize}
			\item If $e_1=[u_1,\dots, u_a]$ then $e_2=[f(u_1),\dots,f(u_a)]$.
			\item If $v_1$ and $v_2$ are the roots of
			$T_1$ and $T_2$ respectively, then $v_2=f(v_1)$.
			\item For any vertex different from the root $u\in e_1$, it is satisfied that
			\[Tree_{(T_1,v_1)}(u)\morph{k} Tree_{(T_2,v_2)}(f(u)).\]
		\end{itemize}
		\item Let $T_1$ and $T_2$ be rooted trees with
		radius at most $r+1$. Then $T_1\morph{k} T_2$ if
		for any chosen $T=T_1$ or $T=T_2$ and any initial edge
		$e\in E(T)$, the "quantity 
		of initial edges $e_1$ from $T_1$ that satisfy
		$(T_1,e_1)\simeq_k (T, e)$" and the "quantity 
		of initial edges $e_2$ from $T_2$ that satisfy
		$(T_2,e_2)\simeq_k (T, e)$" are the same or 
		are both greater than $k-1$.

@@

\begin{lemma}
	Let $H$ be an hypergraph. Then 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
\end{lemma}
\begin{proof}
Given any one-to-one map $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be 
the indicator variable
that takes value one when $f$ defines an monomorphism 
between $H$ and $G_n$ and zero otherwise. 
The probability that $X^H_{n,f}=1$ is exactly
$\prod_{i=1}^t \left(\frac{\beta_i}{n^{a_i-1}}\right)^{e_i(H)}$ which can
be written as $C\cdot n^{-ex(H)-v(H)}$ for some constant
$C$ that does not depend on $f$ nor $n$. Define 
$X^H_n=\sum_{f\in [n]_{V(H)}} X^H_{n,f}$. Then, by definition, the number of 
copies of $H$ in $G_n$ is exactly $X^H_n/|Aut(H)|$.
Taking into account that 
\[
\mathrm{E}[X^H_n]=(n)_{v(H)} \cdot C\cdot n^{-\sum_{i=1}^t (a_i-1)\cdot e_i(H)}= \Theta(n^{-ex(H)}),
\]
the result follows. 
%Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
% $\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
% $\overbar{h}$ be an ordering of the vertices
%in $V(H)$. For any list 
% $\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
%let $X_{\overbar{v}}$ be the random indicator variable
%that takes value $1$ if the natural map 
% $f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
%between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
%with probability
% $ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
% $
%and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
%all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
%copies of $H$ are in $G_n$. Thus, 
%\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
%= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
%\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
%\]
%The expected number of copies of $H$ in $G_n$ is then this last
%expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
%In consequence,
%\begin{align*}
% &\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
%=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
%\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
%=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
%\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
%n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
%\end{align*}
%and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
\end{proof}

As a corollary of last result we get the following:  
\begin{lemma} \label{lem:nocopiesdense}
	Let $H$ be an hypergraph such that $ex(H)>0$. Then
	a.a.s there are no copies of $H$ in $G_n$. 
\end{lemma}  
\begin{proof}
	Because of the previous fact, 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
	\xrightarrow[]{n\to \infty} 0$. An application of the first moment
	method yields the desired result. 
\end{proof}

A similar result that will be useful later is the following:

\begin{lemma}\label{lem:nocopiesfixed}
	Let $\overline{v}:=(v_1,\dots,v_j)\in \N*$.
	Let $H$ be an hypergraph such that $ex(H)>-j$. 
	Then a.a.s there is no copy of $H$ in $G_n$ that
	contains all $v_1,\dots,v_j$. 
\end{lemma} 
\begin{proof}
It is sufficient to show that
\begin{equation}\label{eqn:aux}
\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
\overline{v} \big]\xrightarrow[]{n\to \infty} 0.
\end{equation}
Then, because of a first moment argument the result follows.\par
Suppose that $v(H)\geq j$. Otherwise the statement is trivial. 
As before, given any $f\in [n]_{V(H)}$, let $X^H_{n,f}$ be the random
variable that takes value one if $f$ is a monomorphism from $H$ to $G_n$
and zero otherwise. The probability that $X^H_{n,f}$ takes value one is
$C\cdot n^{-ex(H)-v(H)}$ for some constant $C$ independent from $f$ and $n$. 
Let 
\[ Y^H_{n,\overline{x}}= \sum_{\substack{f\in [n]_{V(H)}\\ 
\overline{x}\subset Im(f)}} X^H_{n,f}.\]
The number of functions $f\in [n]_{V(H)}$ such that $v_1,\dots,v_j\in Im(f)$
is $\Theta(n^{v(H)-j})$. In consequence 
$
\mathrm{E}\big[Y^H_{n,\overline{v}}\big]=\Theta(n^{-ex(H)-j})
$, and 
\[\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n \text{ containing }
\overline{v} \big]=\Theta(n^{-ex(H)-j}).
\]
This, together with $ex(H)>-j$, proves \cref{eqn:aux}. 
\end{proof}

The main theorem of this section is the following
\begin{theorem} \label{thm:simple}
	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
\end{theorem}
	The first moment method alone is not sufficient
	to prove our claim because the amount of dense 
	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
	in general. Thus, we need to prove that it suffices to
	prohibit a finite amount of dense sub-hypergraphs in order
	to guarantee that $G_n$ is $r$-simple.
\begin{lemma}
	Let $H$ be a dense hypergraph of radius $r$.
	Then $H$ contains a dense sub-hypergraph $H^\prime$ 
	with size no greater than
	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
\end{lemma}
\begin{proof}
	Choose $x\in V(H)$. Successively remove from $G$ edges $e$
	such that $d(x, e)$ is maximum until the resulting graph 
	$H^\prime$ has excess no greater than $0$. We have two cases:
	\begin{itemize}[leftmargin=*]
		\item $ex(H^\prime)=-1$. Let $e=[x_1, \dots, x_b]$ be
		the last removed edge and
		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
		For any $j=1,\dots, d$ choose 
		$P_j$ a path of size no greater than $r+1$ joining
		$x$ and $x_{i_j}$ in $H^\prime$.   
		Then $P_1\cup \dots P_d \cup e$ is a dense sub-hypergraph of $H$
		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
		\item $ex(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
		last removed edge. Continue removing the edges of $G^\prime$ 
		that are at maximum distance from $x$ until you obtain 
		$H^{\prime \prime}$ with $ex(H^{\prime\prime})=-1$. Let 
		$e_2=[y_1, \dots, y_{b_2}]$ be the last removed edge this time.
		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
		joining	$x$ and $x_{i_j}$ in $H^\prime$
		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
		and size less than $2r+2 + a$,
		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
	\end{itemize} 
\end{proof}

@@

\begin{proof}
	Because of last lemma there is a constant $R$ such that 
	``$G$ does not contain dense hypergraphs of size bounded by $R$" implies
	that ``$G$ is $r$-simple". Thus,
	\[ \Ln \mathrm{Pr}\big( G_n \text{ is } r \text{-simple}  \big)
	\geq \Ln \mathrm{Pr} \big( G_n \text{ does not contain dense 
	hypergraphs of size bounded by } R\big).\] 
	Because of	\cref{lem:nocopiesdense}, given any individual dense hypergraph,
	the probability that there are no copies
	of it in $G_n$ tends to $1$ as $n$ goes to infinity. Using that
	there are a finite number of dense hypergraphs of size bounded by
	$R$ we deduce that the RHS of last inequality tends to $1$. 
\end{proof}

@@

We define $\Lambda$ and $M$ as the minimal families
of expressions with arguments $\overbar{\beta}$ that satisfy
 the conditions: \textbf{(1)} $1\in \Lambda$, \textbf{(2)} 
for any $b,i\in \N$ with $1\leq i \leq c$,
$b > 0$, and $\lambda_1,\dots, \lambda_{a_i-1}\in \Lambda$,
the expression $(\beta_i/b) \prod_{j=1}^{a_i-1}\lambda_j$
belongs to $M$,  \textbf{(3)}
for any $\mu\in M$ and any $n\in \N$ both
$\mathrm{Poiss}_{\mu}(n)$ and $\mathrm{Poiss}_\mu(\geq n)$ are in $\Lambda$, 
and  \textbf{(4)} for any $\lambda_1,\lambda_2 \in \Lambda$, the
product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
\par
The goal of this section is to show 
that $\mathrm{Pr}[r,\mathcal{T}]$,
as an expression with parameters
$\overbar{\beta}$, belongs to $\Lambda$ for any choice of 
$r$ and $\mathcal{T}$. \par

\begin{lemma}
	Let $\overline{v} \subset \N*$ be a finite set of fixed vertices and let 
	$\sigma(\overline{x})$ be an open formula with no equality such that
	$length(\overline{x})=length(\overline{v})$. 
	Define $G_n^\prime=G_n \setminus E(\overline{v})$. Fix $R\in \N$. 
	\begin{itemize}
		\item Let $A_n$ be the event that $G^\prime_n$ contains a path of size
		at most	$R+1$ between any two vertices $u,w\in \overline{v}$.
		\item Let $B_n$ be the event
		that $G^\prime_n$ contains a cycle of size at most $R+1$ 
		that contains a vertex $u\in \overline{v}$.
	\end{itemize}
	Then $\Ln \mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))=0$, and 
	$\Ln \mathrm{Pr}(B_n \, | \, \sigma(\overline{v})=0$. 
\end{lemma}
\begin{proof}
	Notice that the events $A_n$ and $B_n$ do not concern the possible edges
	induced over $\overline{v}$. In consequence, because edges are independent
	in our random model, 
	$\mathrm{Pr}(A_n \, | \, \sigma(\overline{v}))
	=\mathrm{Pr}(A_n)$ and 
	$\mathrm{Pr}(B_n \, | \, \sigma(\overline{v}))
	=\mathrm{Pr}(B_n)$.\par
	The facts that $\Ln \mathrm{Pr}(A_n)=0$ and 
	$\Ln \mathrm{Pr}(B_n)=0$ follow
	from \cref{lem:nocopiesfixed} using that 
	(1) the excess of any path is greater or equal than $-1$,
	(2) the amount of paths of size at most $R+1$ is finite,
	(3) the excess of any cycle is zero, and (4) the
	amount of cycles of size at most $R+1$ is finite. 
\end{proof}

@@

\begin{theorem} 
	The following are satisfied:
	\begin{itemize}
		\item[(1)] Let $r\in \N$ and let $\mathcal{T}$ be a
		$k$-equivalence class for trees with radii at most $r$.
		Then $\mathrm{Pr}[r,\mathcal{T}]$ exists and is an expression
		in $\Lambda$.
		\item[(2)] Let $\overbar{w}\in \N*$ be a list of different fixed 
		vertices, and let $\phi[\overbar{x}]\in FO[\sigma]$ be an open sentence
		(i.e. with no bounded variables) such that $\overbar{x}$ and $\overbar{w}$
		have the same size. Let $=v_1,\dots,v_k \in \N$ be another 
		list of different vertices that are contained in $\overbar{w}$.
		Let $r_1,\dots,r_k \in \N$ and let $\mathcal{T}_1,\dots \mathcal{T}_k$
		be $k$-equivalence classes for trees such that
		each $\mathcal{T}_i$ has radii bounded by $r_i$. Then
		\[
		\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};r_i) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)= \prod_{i=1}^k \mathrm{Pr}[r_i,\mathcal{T}_i]. \]	
		\item[(3)] 	
	\end{itemize}
	\begin{proof}
		Let $R$ be an upper bound of the radius of $r$ and the 
		$r_i$'s	in the statement. 
		We will prove (1) and (2) together by induction on $R$. \par
		Assume $R=0$. We start by showing that (1) holds. Recall that
		all trees with radius zero are $k$-equivalent. Thus, if
		$\mathcal{T}$ is the unique $k$-equivalence class of trees
		with radius zero
		and $v\in \N$ is a fixed vertex, then
		 \[
		 \mathrm{Pr}[0;\mathcal{T}] = \Ln \mathrm{Pr}\big( 
		 T:=N^{G_n}(v;0) \text{ is a tree, and } (T,v)\in \mathcal{T} \big)
		 =1, 
		 \]
		Indeed, $N^{G_n}(v;0)$ consists of a single vertex for all $n\geq v$,
		and the above equation follows. The expression $1$ belongs to 
		$\Lambda$, so (1) holds. \par
		The case of (2) is analogous. As $R=0$, then $\mathcal{T}_1=\dots=
		\mathcal{T}_k$ are the unique $k$-equivalence class of trees with
		radius zero. Then, given $\sigma, \overbar{w}, v_1,\dots, v_k$ as
		in the statement,
		\[\Ln \mathrm{Pr}\big( \bigwedge_{i=1}^k 
		T_{n,i}=T_n(v_i,\overbar{w};0) \text{ is a tree and } 
		(T_{n,i},v_i)\in \mathcal{T}_i \, | \, \sigma(\overbar{w})
		\big)=1. \]	
		Because of (1), $\mathrm{Pr}[0,\mathcal{T}_i]=1$ for all $i$'s, 
		and (2) holds. \par
		Now let $R>0$ and assume that both (1) and (2) hold for all 
		lesser values of $R$.  \par
